---
title: "Untitled"
author: "Ken Gu"
date: "2017年3月12日"
output: html_document
---
The goal of this report is to predicting manner(class) based on the other variables
First: Model build strategy (how I built my model)
1.1 to select  Classification Trees/ bagging / s latent Dirichlet allocation (LDA) models
1.2 Before execute the prediction function, I use dplyr to read/clean the data

Second: (how I used cross validation)
2.1 Split the training set to 'train' and 'testing' set based on 70% and 30% 

Third: (what you think the expected out of sample error)
3.1 I use all 3 models to predict on the testing set to get the accuracy result

Fourth: (why I make choice on selection model)
4.1 I select the model with the highest accuracy on the testing test.


```{r, echo=FALSE}
library(dplyr)
library(caret)
library(kernlab)
library(ipred)

```



```{r, echo=FALSE}
# Step 1; read and clean data
datatrainfile <- "./pml-training.csv"
datatrainpml <- read.csv (datatrainfile)
datatestfile <- "./pml-testing.csv"
datatestpml <- read.csv (datatestfile)
# Step 1.1: Clean data
# to select only gyros,accel,magnet, and classe observations

datagyrostrain <- dplyr::select (datatrainpml, contains("gyros_"))
dataacceltrain <- dplyr::select (datatrainpml, contains("accel"))
dataacceltrain <- dplyr::select (dataacceltrain, -contains("total"))
dataacceltrain <- dplyr::select (dataacceltrain, -contains("var"))
datamagnettrain <- dplyr::select (datatrainpml, contains("magnet"))
datamagnettrain <- dplyr::select (datamagnettrain, -contains("total"))
datamagnettrain <- dplyr::select (datamagnettrain, -contains("var"))
dataclasstrain <- dplyr::select (datatrainpml, contains("classe"))
datacleantrain <- cbind(datagyrostrain, dataacceltrain, datamagnettrain, dataclasstrain)

datagyrotest <- dplyr::select (datatestpml, contains("gyros_"))
dataacceltest <- dplyr::select (datatestpml, contains("accel"))
dataacceltest <- dplyr::select (dataacceltest, -contains("total"))
dataacceltest <- dplyr::select (dataacceltest, -contains("var"))
datamagnettest <- dplyr::select (datatestpml, contains("magnet"))
datamagnettest <- dplyr::select (datamagnettest, -contains("total"))
datamagnettest <- dplyr::select (datamagnettest, -contains("var"))
dataclasstest <- dplyr::select (datatestpml, contains("classe"))
datacleantest <- cbind(datagyrotest, dataacceltest, datamagnettest, dataclasstest)


# Step 2: Split the data to training set/ testing set inside the training data
inTrain <- createDataPartition(y=datacleantrain$classe, p=0.7, list=FALSE)
training <- datacleantrain[inTrain,]
testing <- datacleantrain[-inTrain,]

# Step 3: Train All models
modelFit1 <- train(classe ~ . , data=training, method='rpart')
modelFit2 <- train(classe ~ . , data=training, method='treebag')
modelFit3 <- train(classe ~ ., data=training, method='lda')

# Step 4: Get the accuracy result for above 3 models
# predict 
pred1 <- predict(modelFit1, testing)
pred2 <- predict(modelFit2, testing)
pred3 <- predict(modelFit3, testing)

ac1 <- c(pred1==testing$classe)
ac2 <- c(pred2==testing$classe)
ac3 <- c(pred3==testing$classe)

confusionMatrix(pred1, testing$classe)
confusionMatrix(pred2, testing$classe)
confusionMatrix(pred3, testing$classe)

```

```
# After comparision, select model 2, as it has the highest accuracy

# Step 5: Predict 20 different test cases

```{r}
predFinal <- predict(modelFit2, datacleantest)
```


